\documentclass{ctexart}
\usepackage{indentfirst}
\setlength{\parindent}{2em}
\setlength{\parskip}{1ex plus 0.5ex minus 0.2ex}
\selectfont
\footnotesize{\footnotesize}
\title{The Internet of Things}
\author{Chaonan Song}
\begin{document}
\maketitle
\par The first paragraph of this article shows that cyber-security is now part of all our lives.Last year many students suffer from cyber fraud and some students even chose to commit suicide.
\par Now a new phase in this contest is emerging: " the internet of things ". This involves embedding miniature computers in objects and connecting them in internet using wireless technology.
\par Such connectivity offers many advantages, you can adjust you house's heating when you are in office or in bed.But it also gives vicious hackers an easy way to stilling massages of people. Because the miniature computers don't have like smart phone, it do not have much processing power or memory,so security software on them tends to be very basic and not advanced. Researchers have found some ways of hacking into some kinds of medical device or cars. I think if the important information , for instance,the information of bank account was stilled, it could be very dangerous.
\par For the companies building the internet of things ,its vulnerability could be costly. If all lost involves personal safety ,consumers will be less tolerant. In order to avoid the terrible things, tech firms have to embrace higher standards.
\par If the internet of things wants to develop further , it must solve the problem of security, otherwise people will not use internet of things items in their lives.    
\end{document}
