\documentclass{ctexart}
\usepackage{indentfirst}
\setlength{\parindent}{2em}
\setlength{\parskip}{1ex plus 0.5ex minus 0.2ex}
\selectfont
\footnotesize{\footnotesize}
\title{My View on Innovation}
\author{Chaonan Song}
\begin{document}
\maketitle
\section{The Importance of Innovation}
\par I'm not sure if you have heard one of Steve Job's famous remarks:
\begin{quote}
"Innovation distinguishes between a leader and a follower"
\end{quote} which stresses the significance of innovation. There is no doubt that innovation can promote the advancement of society and is the most essential quality for anyone who wants to achieve success. With innovation, any progress will be possible; however ,once indulged in conservatism , everything will remain stagnant.
\section{How to be Innovative}
\par Therefore, we must try our best to know how to be innovation. On the one hand, from the standpoint of a nation, the government should encourage innovation and foster the mindset of continuous learning. Only by doing this can our nation achieve new breakthroughs in all walks of individuals, we should enrich our knowledge reserves and arm ourselves with up-to-date knowledge. Only when we are equipped with vast stores of knowledge can we think out different methods when solving a problem.
\par We should always commit it to our memory that innovation is of great significance to us all. In our daily life, we need to cultivate the habit of applying new thoughts and methods into practice.
\end{document}
